Practical Optional Types for Clojure

### 2015-02-07 icfp15-typedclojure.tex
try to type-set the parent example

\begin{lstlisting}
(defn grandparent [^File f]
  (when f
    (let [f (. f (getParent))]
      (when f
        (. (new File f) (getParent))))))
\end{lstlisting}
%(some-> f (.getParent) (File.) (.getParent))

\begin{lstlisting}
(ann parent [(U nil File) -> (U nil String)])
(defn parent [^File f]
  (when f
    (.getParent f)))
\end{lstlisting}

\begin{lstlisting}
(defalias Expr
  (U '{:op :if :test Expr :then Expr :else Expr}
     '{:op :const :val Any} ...))
(defmulti tree-str (fn [e :- Expr] (:op e)))
(defmethod tree-str :if [{:keys [test then else]}] 
  (str (tree-str test) (tree-str then) (tree-str else)))
(defmethod tree-str :const [{:keys [val]}] 
  (str val))
\end{lstlisting}

>>>>

\begin{lstlisting}
(ann parent [(U nil File) -> (U nil File)])
(defn parent [^File f]
  (when f
    (let [s (. f (getParent))]
      (assert s "Expected parent string, got nil")
      (new File s))))
\end{lstlisting}

$$
\abs{\x{}}{\Union{\Nil}{\File}}
{\letexp {\hinted{\File{}}{f}} {f}
  {\ifexp {f} 
    {\letexp {s} {\methodstaticexp {\File{}} {\String{}} {\String{}} {getParent} {f}}
      {\doexp {\ifexp {s}
                {\nil{}}
                {\errorval{input}}}
              {\newstaticexp {\String{}} {\File{}} {\File{}} {s}}}}
    {\nil{}}
}}
              $$

%(some-> f (.getParent) (File.) (.getParent))

%\begin{lstlisting}
%(ann parent [(U nil File) -> (U nil String)])
%(defn parent [^File f]
%  (when f
%    (.getParent f)))
%\end{lstlisting}

\begin{lstlisting}
(defalias Expr
  (U '{:op :if :test Expr :then Expr :else Expr}
     '{:op :const :val Any} ...))
(ann tree-str [Expr -> String])
(defmulti tree-str (fn [e :- Expr] (get :op e)))
(defmethod tree-str :if [{:keys [test then else]}] 
  (str (tree-str test) (tree-str then) (tree-str else)))
(defmethod tree-str :const [{:keys [val]}] 
  (str val))
\end{lstlisting}
